Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-27 sections/approach.tex
Propose a new title. Shorten Introduction (The rest is commented). and remove VSM section in approach

\dan{**** ALERT **** this entire subsection is not needed! Everything in it is well-known and can simply be referenced. I suggest removing it if we need the space.  I have not edited this section .... }
\subsection{Similarity and Dissimilarity Calculation based on VSM}
%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language. In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
To do so, we use VSM which is a model for representing text documents as vectors.
For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
The $w_{t,d}$ value is tf-idf weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $\operatorname{tf}_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.

\begin{equation}
w_{t,d} = \operatorname{tf}_{t,d} \times \log\frac{|D|}{|\{d' \in D \:|\: t \in d'\}|}
\label{eq:tf-idf}
\end{equation}

After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance.

\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product. Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Cosine similarity using Equation \ref{eq:cosine}. The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.

\begin{equation}
\Sim(c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
\label{eq:cosine}
\end{equation}

\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}. We can use this distance as an dissimilarity. Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Euclidian distance using Equation \ref{eq:cosine}. The distance value is ranging $[0,\infty)$ where 0 means these vectors are the same vectors while a more distance means these vectors are less similar.

\begin{equation}
\Dist(m,c) = \|\overrightarrow{V_m} - \overrightarrow{V_c}\| = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
\label{eq:euclid}
\end{equation}

\subsection{Estimating Similarity and Dissimilarity Thresholds}
Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ to classify useful comments and we have the following values:

$\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} and are \textit{actually useful} i.e. true-positives;

$\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} but are \textit{actually useless} i.e. false positives;

$\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model classifies as \textit{useless} but are \textit{actually useful}.

We can now define the following classification  performance measures: 
\begin{equation}
\begin{split}
\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
\\
\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
\\
\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
\end{split}
\label{eq:fmeasure}
\end{equation}

>>>>

%\dan{**** ALERT **** this entire subsection is not needed! Everything in it is well-known and can simply be referenced. I suggest removing it if we need the space.  I have not edited this section .... }
%\subsection{Similarity and Dissimilarity Calculation based on VSM}
%%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language. In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
%For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
%To do so, we use VSM which is a model for representing text documents as vectors.
%For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
%The $w_{t,d}$ value is tf-idf weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $\operatorname{tf}_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.  
%
%\begin{equation}
%w_{t,d} = \operatorname{tf}_{t,d} \times \log\frac{|D|}{|\{d' \in D \:|\: t \in d'\}|}
%\label{eq:tf-idf}
%\end{equation}
%
%After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance. 
%
%
%\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product. Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Cosine similarity using Equation \ref{eq:cosine}. The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.  
%
%\begin{equation}
%\Sim(c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
%\label{eq:cosine}
%\end{equation}
%
%\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}. We can use this distance as an dissimilarity. Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Euclidian distance using Equation \ref{eq:cosine}. The distance value is ranging $[0,\infty)$ where 0 means these vectors are the same vectors while a more distance means these vectors are less similar.
%
%\begin{equation}
%\Dist(m,c) = \|\overrightarrow{V_m} - \overrightarrow{V_c}\| = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
%\label{eq:euclid}
%\end{equation}
%
%\subsection{Estimating Similarity and Dissimilarity Thresholds}
%Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ to classify useful comments and we have the following values:
%
%$\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} and are \textit{actually useful} i.e. true-positives; 
%
%$\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} but are \textit{actually useless} i.e. false positives;
%
%$\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model classifies as \textit{useless} but are \textit{actually useful}. 
% 
%We can now define the following classification  performance measures: 
%\begin{equation}
%\begin{split}
%\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
%\\
%\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
%\\
%\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
%\end{split}
%\label{eq:fmeasure}
%\end{equation}

### 2014-07-27 sections/background.tex
Propose a new title. Shorten Introduction (The rest is commented). and remove VSM section in approach

%\section{Background}
%In this section, we describe MCR process based on Gerrit system. Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques. 
\dan{this section seems to only cover MCR. We could have this be a Background section with this and the other subsequent sections moved to sub-sections}
\section{Modern Code Review Process}

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}. The grey area shows the review process of the system which composed of four main steps. (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system. (2) reviewers examine the proposed code changes for defects or concerns. (3) reviewers provide comments to the author. The author creates a revised proposed change according to the comments then re-submits for review. Then, reviewers will examine the revised proposed change. If the revision is not approved, reviewers provide comments to fix and the process continues until reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).

According to this process, reviewers' comments are the most important factor in determining software quality. In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs. However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers) and frequently comments are superficial or do not clearly identify defects or relevant issues (e.g. design suggestions, coding styles, etc.) for the proposed change and are thus of questionable usefulness. For example a comment may relate to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. "Keep up the good work!"). Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues. Our observations of the Qt project also correspond to this finding. We found some comments are superficial and unhelpful to the proposed changes. For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information. While the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

@@

>>>>

%\section{Background}
%In this section, we describe MCR process based on Gerrit system. Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques. 
%\dan{this section seems to only cover MCR. We could have this be a Background section with this and the other subsequent sections moved to sub-sections}

\section{Modern Code Review Process}

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}. The grey area shows the review process of the system which composed of four main steps. (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system. (2) reviewers examine the proposed code changes for defects or concerns. (3) reviewers provide comments to the author. The author creates a revised proposed change according to the comments then re-submits for review. Then, reviewers will examine the revised proposed change. If the revision is not approved, reviewers provide comments to fix and the process continues until (4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).

@@

According to this process, reviewers' comments are the most important factor in determining software quality. In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs. However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers) and frequently comments are superficial or do not clearly identify defects or relevant issues (e.g. design suggestions, coding styles, etc.) for the proposed change and are thus of questionable usefulness. For example a comment may relate to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!"). Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues. Our observations of the Qt project also correspond to this finding. We found some comments are superficial and unhelpful to the proposed changes. For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information. While the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

### 2014-07-27 sections/introduction.tex
Propose a new title. Shorten Introduction (The rest is commented). and remove VSM section in approach

\section{Introduction}
Software code review is an established cost-effective software quality management practice.
Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industrial and OSS projects.
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find defects and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then propose changes in response to these comments which in turn are reviewed for approval.  Fig. \ref{fig:process} illustrates a typical MCR process.

Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
However, little research exists investigating how the discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that reviewers comments can either positively contribute to the proposed changes (i.e. ``\emph{useful}''), or be a discussion which is out of scope (i.e. ``\emph{useless}'' relative to the proposed changes\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.}).

Since MCR does not require strict guidelines, checklists, or formal processes, some people tend to review and just look for trivial issues (e.g. coding styles, conventions, and process issues), leaving deeper issues undiscussed \cite{Mcintosh}.
This is a concern because lack of useful comments can degrade the cost-effectiveness and perceived utility of MCR.

Current research has focused mostly on the relation between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et. al. \cite{Beller}.
MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014}, and it is painstaking and time consuming to classify the comments in order to perform appropriate quantitative analysis.
Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.  Fig. \ref{fig:example} show typical MCR comments illustrating these issues.

@@

\dan{Much of the following material should be placed in a separate Motivation section} 
In this paper we present a text mining approach to assist in classifying the usefulness of comments.
The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.

Our modest OSS case study has a over 17,000 potentially useful comments.
At an optimistic 5 seconds peer comment classification, we would expect about 24 person-hours of effort.
Furthermore, manual classification is subjective and error-prone.

By introducing some automation support based on objective empirical criteria,
the method we propose here aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.

We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useless} comment as one that does not.
Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.

In our approach, we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
To determine these semantic relationships, we use the Vector Space Model (VSM) and calculate similarity (using cosine similarity) and dissimilarity (using euclidean distance) between the comment and commit message vectors. 
We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.

For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:

\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?

\noindent In addition to addressing the research questions above, the main contributions of this paper are:
\dan{these are more "results" than contributions.... need to reword this!}
\begin{itemize}
\item A practical to apply approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
\item The experimental results show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping). For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful. The remaining 23\% are undetermined and require manual classification. Thus the classification effort is reduced by about 77\%.
\item xx\% of the comments did not have unanimity (i.e. unclear), and of these yy\% were automatically determined to be useful or not useful. Follow up with dissenting assessors found mis-judgement occurred zz\% of the time whereby in retrospect the comment would have had unanimity. This indicates the method is useful in identifying subjective judgement errors. 
\item Of the 23\% not automatically classified (i.e. undetermined), qq\% were unclear. Of the (1-qq)\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear. This indicates the method is useful in identifying chance unanimity errors or group think bias.
\end{itemize} 
%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

>>>>

\section{Introduction}
Software code review is an established cost-effective software quality management practice.
Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industrial and OSS projects.
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find defects in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments which in turn are reviewed for approval.  
%Fig. \ref{fig:process} illustrates a typical MCR process.

Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
However, little research exists investigating how the discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that reviewers comments can either positively contribute to the proposed changes (i.e. ``\emph{useful}''), or be a discussion which is out of scope (i.e. relatively  ``\emph{useless}''  to the proposed changes). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g. coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}. This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.%This is a concern because lack of useful comments can degrade the cost-effectiveness and perceived utility of MCR.

Prior research has focused mostly on the relation between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et. al. \cite{Beller}.
MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014}, and it is painstaking and time consuming to classify the comments in order to perform appropriate quantitative analysis.
Moreover, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.

% Fig. \ref{fig:example} show typical MCR comments illustrating these issues.
%Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.  Fig. \ref{fig:example} show typical MCR comments illustrating these issues.

In this paper, we present a text mining approach to assist in classifying the usefulness of comments.
The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
By introducing some automation support based on objective empirical criteria,
our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Through a case study of Qt project, we address the following research questions:
\begin{description}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{description}

Our contributions are as follows:
\begin{itemize}
\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness based on using semantic similarity.
\item We investigate relationship between usefulness of comments and semantic similarity.
\item We investigate cost-efficient, assurable and scalable of semantic similarity in large open source project based on actual human effort.
\end{itemize}

%%%%%%%%% TEMP %%%%%%%%%
%We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useless}\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.} comment as one that does not.
%Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
%\dan{Much of the following material should be placed in a separate Motivation section} 
%In our approach, we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
%Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
%To determine these semantic relationships, we use the Vector Space Model (VSM) and calculate similarity (using cosine similarity) and dissimilarity (using euclidean distance) between the comment and commit message vectors. 
%We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
%This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.
%
%For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
%For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
%We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
%comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
%
%\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
%\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
%\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?
%
%\noindent In addition to addressing the research questions above, the main contributions of this paper are:
%\dan{these are more "results" than contributions.... need to reword this!}
%\begin{itemize}
%\item A practical approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
%\item The experimental results, which show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
%\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping). For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful. The remaining 23\% are undetermined and require manual classification. Thus the classification effort is reduced by about 77\%.
%\item \TODO{xx}\% of the comments did not have unanimity (i.e. unclear), and of these \TODO{yy}\% were automatically determined to be useful or not useful. Follow up with dissenting assessors found mis-judgement occurred \TODO{zz}\% of the time whereby in retrospect the comment would have had unanimity. This indicates the method is useful in identifying subjective judgement errors. 
%\item Of the 23\% not automatically classified (i.e. undetermined), \TODO{qq}\% were unclear. Of the \TODO{(1-qq)}\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear. This indicates the method is useful in identifying chance unanimity errors or group think bias.
%\end{itemize} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

@@
